\documentclass[14pt]{extarticle} 
\usepackage[utf8]{inputenc}

% --- REMOVE PAGE NUMBERING ---
\pagestyle{empty}

% --- MARGIN SETUP ---
\usepackage[left=0.75in, right=0.75in, top=0.5in, bottom=0.5in]{geometry}

% --- LIST SETTINGS ---
\usepackage{enumitem} 
\setlist[itemize]{leftmargin=1em}
\setlist[enumerate]{leftmargin=1.5em}

\usepackage{parskip} 

% --- CONTROL SECTION FONT SIZE ---
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{}{0em}{}
\titlespacing*{\section}{0pt}{1em}{0.5em} 

% --- FONT SETUP ---
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault} 

% --- CUSTOM COMMAND FOR TITLE ---
\newcommand{\makeRecipeTitle}{
	{\noindent \Large \textbf{Mexican Chicken Marinade}} 
	\par 
	\vspace{-0.75em} 
}

\begin{document}

% ================= PAGE 1 =================
\makeRecipeTitle

\section*{Ingredients}

\begin{itemize}[itemsep=0.2em, label={\raisebox{-0.1ex}{\large\textbullet}}]
	\item Chicken Thighs – 8
	\item Avocado Oil – 1/3 Cup
	\item Chili Powder/Flakes – 1 tsp
	\item Chipotle Paste/Sauce – 3 tsp (e.g., La Costeña)
	\item Cilantro – ½ Cup, chopped
	\item Cumin Powder – 1 tsp
	\item Garlic Powder – 2 tsp
	\item Limes – 2 (juiced)
	\item Onion Powder – 1.5 tbsp
	\item Oregano – 1.5 tbsp
	\item Paprika – 1 tsp
	\item Black Pepper – ½ tsp
	\item Salt/MSG – 1.5 tsp
\end{itemize}

\newpage
\makeRecipeTitle
\section*{Instructions}

\begin{enumerate}[label=\textbf{\arabic*.}, itemsep=0.25em]

	\item \textbf{Make Marinade} \\
	      In a resealable bag or bowl, combine avocado oil, chili powder, chipotle paste, cilantro, cumin, garlic powder, lime juice, onion powder, oregano, paprika, pepper, and salt/MSG. Whisk or shake until dissolved and combined.

	\item \textbf{Marinate Chicken} \\
	      Add the chicken thighs, ensuring they are well coated. Refrigerate for at least 30 minutes (or overnight for deeper flavor).

	\item \textbf{Sear} \\
	      Preheat a cast iron pan to ripping hot heat. Remove chicken from marinade (discard excess). Sear on both sides for 30–60 seconds to get a char.

	\item \textbf{Cook} \\
	      \textbf{Option A (Air Fryer):} Cook at 400$^\circ$F for 12 minutes, flip, then cook for 8 more minutes. \\
	      \textbf{Option B (Oven):} Bake at 400$^\circ$F for 20–25 minutes.

	\item \textbf{Serve} \\
	      Let the chicken rest for a few minutes before serving.

\end{enumerate}

\end{document}
